% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.3 for LaTeX2e
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{subscript}
\lstset{breaklines=true, basicstyle=\scriptsize\ttfamily}

%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads
%\addtocmark{Hamiltonian Mechanics} % additional mark in the TOC
%
%
\mainmatter              % start of the contributions
%
\title{Keeping scientific materials alive and reusable by supporting collaboration}

%
\titlerunning{Keeping scientific materials alive and reusable by supporting collaboration}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Aleix Garrido\inst{1} \and Jose Manuel Gomez-Perez\inst{1} \and Boris Villazon-Terrazas\inst{1}}
%
\authorrunning{Garrido et al.}   % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Panos Alexopoulos, Manolis Wallace}
%
\institute{
iSOCO, Intelligent Software Components S.A., Av. del
Partenon, 16-18, 1-7, 28042, Madrid, Spain,\\
\email{\{agarrido,jmgomez,bvillazon\}@isoco.com}}


\maketitle              % typeset the title of the contribution

%**************************************************************
%**************************************************************
%**************************************************************


\begin{abstract}
Data-intensive scientific knowledge faces many issues such as the decrease of quality of materials and the difficulties on finding relevant information. Those aspects need to be addressed in order to enhance the future of scientific development. This article presents a set of tools focused on reusability of scientific information based on two different aspects: collaboration and search. We present a visual metaphor called Collaboration Spheres which allow search through exploration of scientific social networks based on a combination of people and information objects. This search paradigm is built around the use of customizable contexts that act as intuitive examples conducted by the users. This tool eases collaboration, expert finding and access to relevant information.
\end{abstract}

\section{Introduction}\label{sec:Introduction}
\input{introduction}

%\section{Reuse of scientific work}\label{sec:RelatedWork}
%\input{reusecientificwork}



\section{Reviewer finder}\label{sec:Motivation}
\input{reviewerfinder}

\section{Dataset description}
Vocabularies

\begin{tabular}{ l l l }
  1 & VIVO Ontology & http://vivoweb.org/ontology/core \\
  2 & BIBO Ontology & http://purl.org/ontology/bibo \\
  3 & FAO Geopolotical  & http://aims.fao.org/aos/geopolitical.owl \\
  4 & Vitro Application Ontology  & http://vitro.mannlib.cornell.edu/ns/vitro/0.7 \\
  5 & FOAF  & http://xmlns.com/foaf/0.1 \\
  6 & SKOS  & http://www.w3.org/2004/02/skos/core \\
  7 & iSOCO vocab & http://vocab.isoco.net \\ 
  8 & Event Ontology & http://purl.org/NET/c4dm/event.owl \\       
\end{tabular}

Some stats

\begin{tabular}{ l r  }
  Number of triples & 2605589 \\
  Number of links &   123606  \\
  Number of authors & 12090   \\
  Number of papers & 17386 \\
  Number of topics & 465706 \\
\end{tabular}


%\section{Evaluation}\label{sec:Evaluation}
%\input{evaluation}


\section{Conclusions and Future Work}\label{sec:Conclusions}
\input{conclusions}

%*****************************************************************************************************************



\section*{Acknowledgments}

This work was supported by SmartContent project.
%and PARLANCE (www.parlanceproject.eu, grant number 287615).



% ---- Bibliography ----
%

\bibliography{bibliography}
\bibliographystyle{plain}



\clearpage
\addtocmark[2]{Author Index} % additional numbered TOC entry
\renewcommand{\indexname}{Author Index}
\printindex \clearpage
\addtocmark[2]{Subject Index} % additional numbered TOC entry
\markboth{Subject Index}{Subject Index}
\renewcommand{\indexname}{Subject Index}
\input{subjidx.ind} 
\end{document}
