%introducción
The Reviewer finder is illustrated by a web application that covers the process of finding a good reviewer for a specific article or publication. The process is driven by actions performed by the user while creating different contexts towards his/her final objective. Each action allows the modification of the search parameters in an intuitive way and offers summaries of information that may help on understanding the available resources.\\
\subsection{Interface Description}
The user interface has been designed in order to keep a minimalist layout that makes user experience smooth and simple. The screen is easily divided in four different parts:
\begin{description}
\item[Spheres]The main part displays a set of concentric circles. These circles have two different functionalities. On the one hand, the center of the circles contains the main article for which we are looking for reviewers. Its adjacent circle is the place where search queries are defined through dropping elements from the lists of items(see Lists) for creating contexts. On the other hand the two external circles offer the results of the reviewer finder. The results are small icons that use different colors depending on the relative quality of the recommendation (green for the best results, yellow for medium, and red for weak recommendations). The icon may have a warning sign associated if a conflict of interest (such as previous co-authors or same organization) is detected for the recommended reviewer.
\item[Lists]A total of six lists are loaded on the right side of the screen. They are divided in two columns: authors and articles. Each column has three lists. The lists on the first column are: list of authors of the main article, list of previous co-authors of the main authors and a list of authors which have worked on related topics to the article to be reviewed. The lists on the second column are: articles of the main authors, articles of previous co-authors and topic related articles. All the items of the lists are draggable and can be dropped on the Spheres in order to customize the context.
\item[Tag Cloud]A tag cloud that gathers the most representative topics of the contexts that are created by the user is placed beneath the Spheres. The tag cloud allows the understanding of the search and results at a glance.
\item[Information box]Each element of the lists and the spheres is clickable. If they are clicked, a box of information placed on the right-bottom corner of the screen loads a brief summary of information, together with a link to its uri and a list of relevant topics for the current context.
\end{description}
\subsection{Basic Architecture}
blablabla
\subsection{Scenario}
In this scenario the editor in chief of the Journal of Personality and Social Psychology\footnote{\url{http://www.apa.org/pubs/journals/psp/}} is trying to select reviewers for a submission they have just received. The first step will be to open the collaboration spheres for that Article: 
\begin{itemize}
  \item The selected Article is called "Attachment change processes in the early years of marriage" \footnote{\url{http://vivo.apa.org/individual/n61963}}.
  \item Then we can launch the Collaboration Spheres for the Article \footnote{\url{http://apaproject.isoco.com/index.html?id=http://vivo.apa.org/individual/n61963}}.
\end{itemize}
As we can see, at the tag cloud shows the most relevant topics for the Article placed in the center of the Collaboration Spheres and we get a preliminary set of recommended reviewers for it.\\
Since we want to define a bit better the topics for our context, i.e. the special issue, and, in order to get better recommendations, we will add an article of our interest (can be found at the “Articles by Topic section), which is very related to the topics of the special issue. We select the following article in the “Articles by topic” panel on the right and drag and drop it into the blue circle of the context of interest:
\begin{itemize}
  \item The added article is "Adult attachment and the transition to parenthood" \footnote{\url{http://vivo.apa.org/individual/n5724}}.
\end{itemize}
Now the editor in chief will include some of the members of the Editorial Board (Interpersonal Relations and Group Processes Section\footnote{\url{http://www.apa.org/pubs/journals/psp/edboard-irgp.aspx}}), who will serve as exemplars of the knowledge required to properly evaluate the submissions which are received. Suitable reviewers will therefore be knowledgeable of (part of) those topics. This way we increase the alignment between the related topics in the expertise of our editors and the recommended experts for reviewing the article. In this case, the editor in chief adds:
\begin{itemize}
  \item Consulting Editors:
  \begin{itemize}
    \item Bolger, Niall\footnote{\url{https://vivo.apa.org/display/n41433}}
    \item Algoe, Sara B.\footnote{\url{https://vivo.apa.org/display/n59044}}
  \end{itemize}
  \item Associate Editors:
  \begin{itemize}
      \item Finkel, Eli J.\footnote{\url{https://vivo.apa.org/display/n36079}}
      \item Gable, Shelly L.\footnote{\url{https://vivo.apa.org/display/n37385}}
  \end{itemize}
\end{itemize}
We can see at every addition how the main topics change in the tag cloud and how the recommendations are adjusted to the context. When the editor in chief adds the last of the associate editors, the relevance of the different related topics seems to be uniformly distributed. The editor in chief then may want to reconsider the composition of the board and replace some of the editors (e.g. Gable with another expert with knowledge about other topics more, which the editor in chief finds especially relevant for the special issue).  In this case, the editor in chief selects an author who brings in expertise related to topics like alcohol abuse:
\begin{itemize}
  \item Zywiak, William H.\footnote{\url{https://vivo.apa.org/display/n8844}}
\end{itemize}
In addition to the summary that we provide for each author and article, the system can also launch a Twitter search that covers his/her/its intersection with the most relevant topics of the context of interest.
